---
title: "DryBeanFinal"
author: "Devon"
date: "May 6, 2016"
output: html_document
---

Agglomerative, Hierarchical Clustering
based on Standardized Data, Goodness of fit
```{r}
library(scales)
library(ggplot2)
library(plyr)
library(vegan)
library(cluster)
library(ade4)
library(stats)
#install.packages("ade4")
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & !(Y$Var=="Z"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwghttrial),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE),
            meanemerge = mean(emergetrial, na.rm=TRUE)))
Dend<-scale(as.matrix(Y4 [,c("meanwght", "meanlngth", "meanarea", "meanemerge")]))    
rownames(Dend)=Y4$Title
bray <- (dist(Dend, method = "maximum", diag = FALSE, upper = FALSE))
bray.v<-as.vector(bray)
bray.dis <- agnes(bray, method="average", diss = TRUE) 
bray.disv<-as.vector(bray.dis)
# very simple dendrogram
plot(bray.dis)
#Cophenetic Distances and Correlation
bray.ave.co <- cophenetic(bray.dis)
# vectorize the cophenetic distances
bray.ave.cov <- as.vector(bray.ave.co) 
cor(bray.ave.cov, bray.v)
plot(y = bray.ave.cov, x = bray.v)

#Mantel Test
mant1 <- mantel.rtest(bray, bray.ave.co, nrepet=1000)
plot(mant1)
summary(mant1)

#RMSE
rmse <- function(x, dis.matrix){
 r.m.s.e <- 1- (mean(as.vector(x)^2))/var(as.vector(dis.matrix))
 return(r.m.s.e)
}
bray.co.resid <- bray.ave.cov - bray.v
rmse(bray.co.resid, bray.v)
```


Agglomerative, Hierarchical Clustering
based on Standardized Data, Chord
```{r}
library(scales)
library(ggplot2)
library(plyr)
library(vegan)
library(cluster)
library(ade4)
library(stats)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & !(Y$Var=="Z"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwghttrial),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE),
            meanemerge = mean(emergetrial, na.rm=TRUE)))
Dend<-scale(as.matrix(Y4 [,c("meanwght", "meanlngth", "meanarea", "meanemerge")]))    
rownames(Dend)=Y4$Title
chord = function (s,diag) {
  # G.Nesslage, B.Maurer
  # computes chord distance
  # diag == TRUE returns full distance matrix
  # diag == FALSE returns distance matrix as dist object
  n = nrow(s)
  p <- ncol(s)
  D = matrix(0,n,n)
  m <- 1
  
  for (i in 1:(n-1)){
    for (j in (i+1):n){
      nd <- matrix(0,p,1)
      dd1 <- matrix(0,p,1)
      dd2 <- matrix(0,p,1)
      for (k in 1:p){
        nd[k,]<- s[i,k]*s[j,k]
        dd1[k,] <- (s[i,k])^2
        dd2[k,] <- (s[j,k])^2
      }
      D[i,j] <- sqrt(2*(1-(sum(nd)/sqrt(sum(dd1)*
                                          sum(dd2)))))
      D[j,i] <- D[i,j]
    }
  }
  
  if(diag==FALSE) {D=as.dist(D)}
  return (D)
}
rownames(Dend)=Y4$Title
chord1 <- chord(Dend,diag=FALSE)
chord.v <- as.vector(chord1)
label <- rownames(Dend)
chord.dis <- agnes(chord1, method="average", diss = TRUE) 
chord.disv<-as.vector(chord.dis)
# very simple dendrogram
plot(chord.dis, ask = FALSE, which.plots = 2,labels = label)

#Cophenetic Distance and Correlation
chord.ave.co <- cophenetic(chord.dis)
chord.ave.cov <- as.vector(chord.ave.co)
cor(chord.ave.cov, chord.v)
plot(y = chord.ave.cov, x = chord.v)

#RMSE
rmse <- function(x, dis.matrix){
 r.m.s.e <- 1- (mean(as.vector(x)^2))/var(as.vector(dis.matrix))
 return(r.m.s.e)
}
chord.co.resid <- chord.ave.cov - chord.v
rmse(chord.co.resid, chord.v)

#Bray doesn't work with negative values
#bray.dis <- vegdist(as.matrix(Dend), method = "bray")
#bray.ave.dis <- agnes(bray.dis, diss = TRUE) 
#plot(bray.ave.dis, ask = FALSE, which.plots = 2,labels = label)

#canberra doesn't work with negative values
#bray.dis <- vegdist(as.matrix(Dend), method = "brayberra")
#bray.ave.dis <- agnes(bray.dis, diss = TRUE) 
#plot(bray.ave.dis, ask = FALSE, which.plots = 2,labels = label)
#bray.ave.co <- cophenetic(bray.ave.dis) 
#bray.ave.cov <- as.vector(bray.ave.co) # vectorize the cophenetic distances
```

Agglomerative, Hierarchical Clustering
Dendogram based on Raw Data Relative to Trial
```{r}
library(scales)
library(ggplot2)
library(plyr)
library(vegan)
library(cluster)
library(ade4)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & !(Y$Var=="Z"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwght, na.rm=TRUE),
            meanlngth = mean(rtlngth, na.rm=TRUE),
            meanarea = mean(rtarea, na.rm=TRUE)))
Dend<-as.matrix(Y4 [,c("meanwght", "meanlngth", "meanarea")])
rownames(Dend)=Y4$Title
bray <- (vegdist(Dend, method = "bray", diag = FALSE, upper = FALSE))
bray.v <- as.vector(bray)
#print(bray)
bray.v<-as.vector(bray)
#print(bray.v)           
bray.dis <- agnes(bray, method="ward", diss = TRUE) 
bray.disv<-as.vector(bray.dis)
# very simple dendrogram
plot(bray.dis)

#Cophenetic Distances and Correlation
bray.ave.co <- cophenetic(bray.dis)
bray.ave.cov <- as.vector(bray.ave.co) # vectorize the cophenetic distances
cor(bray.ave.cov, bray.v)
plot(y = bray.ave.cov, x = bray.v)

#Mantel Test
mant1 <- mantel.rtest(bray, bray.ave.co, nrepet=1000)
plot(mant1)
mant1

#RMSE
rmse <- function(x, dis.matrix){
 r.m.s.e <- 1- (mean(as.vector(x)^2))/var(as.vector(dis.matrix))
 return(r.m.s.e)
}
bray.co.resid <- bray.ave.cov - bray.v
rmse(bray.co.resid, bray.v)

```



Divisive Clustering
Raw Data Relative to Trial
```{r}
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwght, na.rm=TRUE),
            meanlngth = mean(rtlngth, na.rm=TRUE),
            meanarea = mean(rtarea, na.rm=TRUE), meanemerge = mean(Emerge, na.rm=TRUE)))
Dend<-scale(as.matrix(Y4 [,c("meanwght", "meanlngth", "meanarea", "meanemerge")]))
rownames(Dend)=Y4$Title
k.pot <- kmeans(as.matrix(Dend),5,100)
k.pot$cluster
as.matrix(k.pot$cluster)

```   

```
library(d3heatmap)
library(stats)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCup.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwght, na.rm=TRUE),
            meanlngth = mean(rtlngth, na.rm=TRUE),
            meanarea = mean(rtarea, na.rm=TRUE), meanemerge = mean(Emerge, na.rm=TRUE)))
stuff<-cbind(Y4$meanwght, Y4$meanlngth, Y4$meanarea, Y4$meanemerge)
rownames(stuff)<-Y4$Title

d3heatmap(stuff, scale = "column", labCol=c("Root dry weight", "Root length", "Root area", "Emergence"), cexCol=0.6, cexRow = 0.8, distfun=chord, hclustfun=hclust, Colv=as.dendogram(hc.rows), dendrogram = "row",
    color = "Blues")
as.dendogram(hc.rows)

```


```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & (Y$Var=="RH"))
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "tisolate"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE), meanemerge = mean(emergetrial, na.rm=TRUE)))
stuff<-cbind(Y4$meanwght, Y4$meanlngth, Y4$meanarea, Y4$meanemerge)
rownames(stuff)<-Y4$tisolate
colnames(stuff)<-c("Root Dry Weight", "Root Length", "Root Area", "Emergence")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE, fontsize_row=9,
         #cluster_rows=hc.rows, 
         clustering_method="average")

```

Heatmap of 4 Cup Assay Variables No Chord - default
```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & (Y$Var=="Z"))
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE), meanemerge = mean(emergetrial, na.rm=TRUE)))
stuff<-cbind(Y4$meanwght, Y4$meanlngth, Y4$meanarea, Y4$meanemerge)
rownames(stuff)<-Y4$Title
colnames(stuff)<-c("Root Dry Weight", "Root Length", "Root Area", "Emergence")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         #cluster_rows=hc.rows, 
         clustering_method="average")

```


Heatmap of 4 Cup Assay Variables with CHORD
```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & (Y$Var=="RH"))
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE), meanemerge = mean(emergetrial, na.rm=TRUE)))
stuff<-cbind(Y4$meanwght, Y4$meanlngth, Y4$meanarea, Y4$meanemerge)
rownames(stuff)<-Y4$Title
colnames(stuff)<-c("Root Dry Weight", "Root Length", "Root Area", "Emergence")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE, fontsize_row=9,
         #cluster_rows=hc.rows, 
         clustering_method="average")

```


```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCupApr19.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & (Y$Var=="Z"))
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwght),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE), meanemerge = mean(emergetrial, na.rm=TRUE)))
stuff<-cbind(Y4$meanwght, Y4$meanlngth, Y4$meanarea, Y4$meanemerge)
rownames(stuff)<-Y4$Title
chord = function (s,diag) {
  # G.Nesslage, B.Maurer
  # computes chord distance
  # diag == TRUE returns full distance matrix
  # diag == FALSE returns distance matrix as dist object
  n = nrow(s)
  p <- ncol(s)
  D = matrix(0,n,n)
  m <- 1
  
  for (i in 1:(n-1)){
    for (j in (i+1):n){
      nd <- matrix(0,p,1)
      dd1 <- matrix(0,p,1)
      dd2 <- matrix(0,p,1)
      for (k in 1:p){
        nd[k,]<- s[i,k]*s[j,k]
        dd1[k,] <- (s[i,k])^2
        dd2[k,] <- (s[j,k])^2
      }
      D[i,j] <- sqrt(2*(1-(sum(nd)/sqrt(sum(dd1)*
                                          sum(dd2)))))
      D[j,i] <- D[i,j]
    }
  }
  
  if(diag==FALSE) {D=as.dist(D)}
  return (D)
  
}
chord1 <- chord(stuff,diag=FALSE)
hc.rows<-hclust(chord1, method="average")
colnames(stuff)<-c("Root Dry Weight", "Root Length", "Root Area", "Emergence")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         cluster_rows=hc.rows, 
         clustering_method="average")

```

Seed Rot
```{r}
library(pheatmap)
library(plyr)
library(ggplot2)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllRotMay9.csv"))
Y3<-subset(Y, !(Y$SevPercent=="NA") & (Y$Var=="Z"))
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "tisolate"), summarise,
               N    = length(SevPercent),
            meansp = mean(SevPercent, na.rm=TRUE),
            means = mean(Sev, na.rm=TRUE)))
stuff<-as.data.frame(cbind(Y4$meansp, Y4$means))
rownames(stuff)<-Y4$tisolate
colnames(stuff)<-c("Severity, as Percent", "severity")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         #cluster_rows=hc.rows, 
         clustering_method="average")
```


Seed Rot Zorro, two temperatures
```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllRotMay9.csv"))
Y20<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="Z") & Y$Temp=="20")
Y26<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="Z") & Y$Temp=="26")
Sev26<-Y26$SevPercent
Y3<-cbind(Y20, Sev26)
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(SevPercent),
            sev20 = mean(SevPercent, na.rm=TRUE),
            sev26 = mean(Sev26, na.rm=TRUE)))
stuff<-as.data.frame(cbind(Y4$sev20, Y4$sev26))
rownames(stuff)<-Y4$Title
colnames(stuff)<-c("Severity 20C", "Severity 26C")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         #cluster_rows=hc.rows, 
         clustering_method="average")

```

Seed Rot Red Hawk, two temperatures
```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllRotMay9.csv"))
Y20<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="RH") & Y$Temp=="20")
Y26<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="RH") & Y$Temp=="26")
Sev26<-Y26$SevPercent
Y3<-cbind(Y20, Sev26)
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(SevPercent),
            sev20 = mean(SevPercent, na.rm=TRUE),
            sev26 = mean(Sev26, na.rm=TRUE)))
stuff<-as.data.frame(cbind(Y4$sev20, Y4$sev26))
rownames(stuff)<-Y4$Title
colnames(stuff)<-c("Severity 20C", "Severity 26C")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         #cluster_rows=hc.rows, 
         clustering_method="average")

```


Seed Rot, Red Hawk, Clade, Two Temperatures
```{r}
library(pheatmap)
library(plyr)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllRotMay9.csv"))
Y$Clade<-as.factor(Y$Clade)
Y20<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="RH") & Y$Temp=="20")
Y26<-subset(Y, #!(Y$SevPercent=="NA") & 
              (Y$Var=="RH") & Y$Temp=="26")
Sev26<-Y26$SevPercent
Y3<-cbind(Y20, Sev26)
Y3$tisolate<-paste(Y3$Title,Y3$Trt)
Y4<-( ddply(Y3, c("Var", "Clade"), summarise,
               N    = length(SevPercent),
            sev20 = mean(SevPercent, na.rm=TRUE),
            sev26 = mean(Sev26, na.rm=TRUE)))
            sev20se=
            sev26se=
stuff<-as.data.frame(cbind(Y4$sev20, Y4$sev26))
rownames(stuff)<-Y4$Clade
colnames(stuff)<-c("Severity 20C", "Severity 26C")
pheatmap(stuff, show_rownames = TRUE, show_colnames = TRUE,
         #cluster_rows=hc.rows, 
         clustering_method="average")
plot(stuff$`Severity 20C`)

```





```


```{r}
library(scales)
library(ggplot2)
library(plyr)
library(vegan)
library(cluster)
library(ade4)
library(stats)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/DryBean/AllCup.csv"))
Y3<-subset(Y, !(Y$rtarea=="NA") & !(Y$rtwght=="NA") & !(Y$Var=="Z"))
Y4<-( ddply(Y3, c("Var", "Title"), summarise,
               N    = length(rtwghttrial),
            meanwght = mean(rtwghttrial, na.rm=TRUE),
            meanlngth = mean(rtlngthtrial, na.rm=TRUE),
            meanarea = mean(rtareatrial, na.rm=TRUE),
            meanemerge = mean(emergetrial, na.rm=TRUE)))
Dend<-scale(as.matrix(Y4 [,c("meanwght", "meanlngth", "meanarea", "meanemerge")]))    
rownames(Dend)=Y4$Title
chord = function (s,diag) {
  # G.Nesslage, B.Maurer
  # computes chord distance
  # diag == TRUE returns full distance matrix
  # diag == FALSE returns distance matrix as dist object
  n = nrow(s)
  p <- ncol(s)
  D = matrix(0,n,n)
  m <- 1
  
  for (i in 1:(n-1)){
    for (j in (i+1):n){
      nd <- matrix(0,p,1)
      dd1 <- matrix(0,p,1)
      dd2 <- matrix(0,p,1)
      for (k in 1:p){
        nd[k,]<- s[i,k]*s[j,k]
        dd1[k,] <- (s[i,k])^2
        dd2[k,] <- (s[j,k])^2
      }
      D[i,j] <- sqrt(2*(1-(sum(nd)/sqrt(sum(dd1)*
                                          sum(dd2)))))
      D[j,i] <- D[i,j]
    }
  }
  
  if(diag==FALSE) {D=as.dist(D)}
  return (D)
}
rownames(Dend)=Y4$Title
chord1 <- chord(Dend,diag=FALSE)
chord.v <- as.vector(chord1)
label <- rownames(Dend)
chord.dis <- agnes(chord1, method="average", diss = TRUE) 
chord.disv<-as.vector(chord.dis)
# very simple dendrogram
plot(chord.dis, ask = FALSE, which.plots = 2,labels = label)
hc.rows<-hclust(chord1, method="average")
colnames(Dend)<-c("Root Dry Weight", "Root Length", "Root Area", "Emergence")
pheatmap(Dend, show_rownames = TRUE, show_colnames = TRUE,
         cluster_rows=hc.rows, 
         clustering_method="average")
```

Y5<-( ddply(Y4, c("Var", "Title"), summarise,     
            scalewght=scale(meanwght, center=TRUE, scale=TRUE),
scalelngth=scale(meanlngth, center=TRUE, scale=TRUE),
scalearea=scale(meanarea, center=TRUE, scale=TRUE),
scaleemerge=scale(meanemerge, center=TRUE, scale=TRUE)))
sdrtwght   = sd(rtwght),
            sdrtlngth=sd(rtlngth),
            sdrtarea=sd(rtarea),
            sdemerge=sd(Emerge),
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
