---
title: "FinalStats"
author: "Devon"
date: "May 11, 2016"
output: html_document
---

#Model Fitting
```{r, echo=FALSE}
library(lme4)
library(stats)
library(Rmisc)
library(ggplot2)
rm(list = ls())
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CADnoCON.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") & !(Y$sdtrt=="CON") 
           #& !(Y$Year=="2013")
           )
Y3$stcost <- ifelse(Y3$sdtrt == "F", 4, ifelse((Y3$sdtrt =="F+I"), 10, 20))
Diff<-function(x){
  cry<-(Y3$stcost/(Y3$yield*x))
  diff<-(Y3$RR-cry)
  return(diff)
}
output<-as.data.frame(NULL)
for(i in c(6,10,14)){
DIFF<-Diff(i)
output_i<-cbind.data.frame(Y3, DIFF, i)
output<-rbind.data.frame(output,output_i)
}
output$soycost<-as.numeric(output$i)
output$Diff<-as.numeric(output$DIFF)
D<-output
D$N<-D$Diff
D$N <- ifelse(D$N < 0, 0, ifelse((D$N > 0), 1, 1))
D$var <- as.factor(D$var)
D$soycostsc<-scale(D$soycost)

#Accounting for similarities in Density Plot
hist1<-as.data.frame(cbind(D$N, D$location, D$Year, D$sdtrt))
H1<-subset(hist1, D$location=="HIL")
I1<-subset(hist1, D$location=="IN2")
colnames(H1)=c("N", "location", "Year", "sdtrt")
colnames(I1)=c("N", "location", "Year", "sdtrt")
g1<-ggplot(data=H1, aes(x=N))+
  geom_histogram()
g2<-ggplot(data=I1, aes(x=N))+
  geom_histogram()
multiplot(g1, g2, cols=2)

#Random Effects Fitting for BINOMIAL Distribution
a1 <- glmer(N ~ soycostsc + sdtrt + (1|sdtrt:YL) + (1|var) + (1|sdtrt:var) + (1 | rep/YL), data=D, family=binomial)
a2 <- glmer(N ~ soycostsc + sdtrt + (1|sdtrt:YL) + (1|var) + (1 | rep/YL), data=D, family=binomial)
a3 <- glmer(N ~ soycostsc + sdtrt + (1|var) + (1 | rep/YL), data=D, family=binomial)
a4 <- glmer(N ~ soycostsc + sdtrt + (1 | rep/YL), data=D, family=binomial)
atest<-anova(a1, a2, a3, a4)
print(atest)

#Random Effects Fitting for Proc Mixed
a1 <- lmer(phcont ~ soycostsc + sdtrt + (1|sdtrt:YL) + (1|var) + (1|sdtrt:var) + (1 | rep/YL), data=D)
a2 <- lmer(phcont ~ soycostsc + sdtrt + (1|sdtrt:YL) + (1|var) + (1 | rep/YL), data=D)
a3 <- lmer(phcont ~ soycostsc + sdtrt + (1|var) + (1 | rep/YL), data=D)
a4 <- lmer(phcont ~ soycostsc + sdtrt + (1 | rep/YL), data=D)
atest<-anova(a1, a2, a3, a4)
print(atest)


#Fixed Effects Model Fitting for MLE
f1 <- glmer(N ~ soycostsc + sdtrt +var+ sdtrt:var+ location + sdtrt:location+ (1 | rep/location), data=D, family=binomial)
f2 <- glmer(N ~ soycostsc + sdtrt +var+ location + sdtrt:location+ (1 | rep/location), data=D, family=binomial)
f3 <- glmer(N ~ soycostsc + sdtrt +var+ location + (1 | rep/location), data=D, family=binomial)
f4 <- glmer(N ~ soycostsc + sdtrt + location + (1 | rep/location), data=D, family=binomial)
f5<-glmer(N ~ location + sdtrt + (1 | rep/location), data=D, family=binomial)
ftest<-anova(f1, f2, f3, f4, f5)
print(ftest)

#Fixed Effects Model Fitting for MLE
t1 <- lmer(yieldcont ~ sdtrt + var+ sdtrt:var+ location + (1 | rep/location), data=D)
t2 <- lmer(yieldcont ~ sdtrt + (1|var)+(1|sdtrt:var)+ (1|sdtrt:location) + (1 | rep/location), data=D)
gtest<-anova(t1, t2)
print(gtest)
```

#Produce CSV of Mean RR and Predicted Prob, by factors
```{r, echo=FALSE}
library(lme4)
library(aod)
library(Rcpp)
library(ggplot2)
library(plyr)
library(Rmisc)
library(scales)
library(Hmisc)
library(drc)
library(AICcmodavg)
library(multcomp)
library(nlme)
library(fields)
rm(list = ls())
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CADnoCON.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") & !(Y$sdtrt=="CON") 
           #& !(Y$Year=="2013")
           )
Y3$stcost <- ifelse(Y3$sdtrt == "F", 4, ifelse((Y3$sdtrt =="F+I"), 10, 20))
Diff<-function(x){
  cry<-(Y3$stcost/(Y3$yield*x))
  diff<-(Y3$RR-cry)
  return(diff)
}
output<-as.data.frame(NULL)
for(i in c(6,10,14)){
DIFF<-Diff(i)
output_i<-cbind.data.frame(Y3, DIFF, i)
output<-rbind.data.frame(output,output_i)
}
output$soycost<-as.numeric(output$i)
output$Diff<-as.numeric(output$DIFF)
D<-output
D$N<-D$Diff
D$N <- ifelse(D$N < 0, 0, ifelse((D$N > 0), 1, 1))
D$var <- as.factor(D$var)
D$soycostsc<-scale(D$soycost)
D$Low5wksc<-scale(D$Low5wk)
mprob <- glmer(N ~ soycostsc + location + sdtrt + var + (1 | YL:rep), data=D, family=binomial)
summary (mprob)
BIC(mprob)

predictglm<-predictSE.merMod (mprob, D, se.fit = TRUE, type = "link", level=0, print.matrix = FALSE) 
Dglm <- cbind(D, predictglm)
Dglm <- within(Dglm, {
  PredictedProb <- plogis(fit)
  LL <- plogis(fit - (1.96 * se.fit))
  UL <- plogis(fit + (1.96 * se.fit))
  }
)
write.csv(Dglm, ("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/P/ProbFull.csv"))

Dglmprob <-( ddply(Dglm, c("soycost", "location", "var", "sdtrt"), summarise,
            RRmean=mean(RR),
               meanProb = mean(PredictedProb),
            meanN6=mean(N),
            ULmean=mean(LL),
              LLmean=mean(UL)))


write.csv(Dglmprob, ("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/P/Prob.csv"))

```

#Correlation Plots
```{r, echo=FALSE}
library(lme4)
library(aod)
library(Rcpp)
library(ggplot2)
library(plyr)
library(Rmisc)
library(scales)
library(Hmisc)
library(drc)
library(pbkrtest) 
library(fields)
library(arm)
library(AICcmodavg)
library(multcomp)
library(nlme)
library(corrplot)
#update.packages("corrplot")
#install.packages("corrplot")
rm(list = ls())

#Overall
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") #& !(Y$sdtrt=="CON") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot(corr2, method="number")
corr1<-rcorr(Y5, type="pearson")
#print(corr1)

#Allegan
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="ALE") 
           & (Y$Year=="2015")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#Hillsdale
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="HIL") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#Ingham
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="IN2") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#Lenawee
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="LEN") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#Saginaw
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="SAG") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#Sanilac
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="SAN") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)

#St. Joseph
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles//CADMay17.csv"))
Y3<-subset(Y, !(Y$Diff=="NA") & !(Y$location=="STJ") 
           #& !(Y$Year=="2013")
           )
Y5<-as.matrix(cbind(Y3$yieldcont, Y3$PRha, Y3$Scpubcont, Y3$RDW, Y3$PD, Y3$Low5wk, Y3$ac))
colnames(Y5) <- c("Yield", "Partial Returns", "Plant Stand", "Root Dry Weight", "Planting Date", "Low Temps", "Aphid Counts")
corr2<-cor(Y5, use="pairwise.complete.obs")
corrplot.mixed(corr2)
```

#Useful CorrPlots
```{r, echo=FALSE}
library(ggplot2)
library(plyr)
library(Rmisc)
library(scales)
library(HSAUR)
library(Hmisc)
library(arm)
library(corrplot)
library(graphics)
#update.packages("corrplot")
#install.packages("corrplot")
rm(list = ls())
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/LocationYearData.csv"))
Y3<-subset(Y, Y$Sdtrt=="Overall")
Y5<-as.matrix(cbind(Y3$Yieldcont, Y3$PRha, Y3$RR, Y3$Scpubcont, Y3$pH, Y3$CEC, Y3$SOM, Y3$Sand, Y3$Clay, Y3$Low5wk, Y3$RF2wk, Y3$PD))
colnames(Y5) <- c("Yield", "PR", "RR", "Stand", "pH", "CEC", "SOM", "Sand %",  "Clay %", "Low5wk", "RF2wk", "PD")
corr2<-cor(Y5, use="pairwise.complete.obs")
Y6<-as.data.frame(Y5)
plot(Y6)
dev.off()
corrplot.mixed(corr2, tl.offset = 0, tl.pos="d", tl.cex=0.8)
corr1<-rcorr(Y5, type="pearson")
#print(corr1)
```


#Density Plot for SoySeedTrt
```{r, echo=FALSE}
library(ggplot2)
library(plyr)
rm(list = ls())
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/P/ProbFull.csv"))
y3<-subset(Y, (Y$soycost=="10"))
y4 <-( ddply(y3, c("location", "sdtrt"), summarise,
            meanProb=mean(PredictedProb),
            medianProb=median(PredictedProb)))
g<-ggplot(y3, aes(x=PredictedProb))
g+
  #geom_histogram(aes(y=..density..),bins=20)+
  theme_light()+
  geom_density(adjust=2)+
geom_vline(data=y4, aes(xintercept=meanProb, color="Median"))+ 
  geom_vline(data=y4, aes(xintercept=medianProb, color="Mean"))+
facet_grid(location~sdtrt)+
  theme(axis.text=element_text(size=7))+
  labs(x="Predicted Probability of Breaking Even", y="Density", color="Averages")+
  scale_x_continuous(limits=c(0,1), breaks=c(0.1,0.2,0.3,0.4, 0.5, 0.6,0.7,0.8,0.9))
```

#Field Isolate Chart
```{r, echo=FALSE}
library(ggplot2)
library(Rmisc)
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/FieldIsolates_May24.csv"))
YO<-subset(Y, !(Species=="") & (Pathogen=="O"))
YF<-subset(Y, !(Species=="") & (Pathogen=="F"))
     
    g1<-ggplot(YO, aes(x=Spec))+
geom_bar(data=YO, aes(fill=Location))+ 
theme_light()+
theme(axis.text=element_text(angle=90, hjust=1, vjust=0.5, size=12))+
labs(x="", y="Number of Isolates")+
ylim(0, 30)

     g2<-ggplot(YO, aes(x=Spec))+
geom_bar(data=YF, aes(x=Spec, fill=Location))+
theme_bw()+
theme(axis.text=element_text(angle=90, hjust=1, vjust=0.5, size=12))+
labs(x="", y="Number of Isolates")+ 
ylim(0, 30)

multiplot(g1, g2, cols=1)

```


#Greenhouse and Field Emergence/RDW Comparisons
```{r, echo=FALSE}
library(ggplot2)
library(lsmeans)
library(lme4)
library(Rmisc)
rm(list = ls())
#2015
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CAD.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") #& !(Y$sdtrt=="CON") 
           & (Y$Year=="2015") 
           )
Y3$var<-as.factor(Y3$var)
lm1<-lmer(Scpubcont ~ sdtrt*var*YL + (1 | rep/YL), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt:var | var)
a<-as.data.frame(summary(lsm1$lsmeans))
a12<-subset(a, !(a$var=="3") & !(a$var=="4"))

g<-ggplot(a12, aes(y=lsmean, x=var, color=sdtrt)
)+
  geom_point(position=position_dodge(width=0.21))+
   geom_errorbar(aes( ymin=a12$lsmean-1.96*a12$SE, ymax=a12$lsmean+1.96*a12$SE), width=0.2, position=position_dodge(width=0.21))+
  labs(y="Field Emergence \n Relative to NTC", x="Soybean Variety", color="Seed Treament")+
theme(axis.title=element_text(size=14), axis.text=element_text(size=12), legend.title=element_text(size=14), legend.text=element_text(size=12))
  
#GH
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/GHData.csv"))
Y3<-subset(Y, !(Y$RDWcont=="NA") & !(Y$Var=="Sloan")
           #& (Y$PathTitle=="Control") 
           #& !(Y$sdtrt=="CON")
           )
Y3$Var<-as.factor(Y3$Var)
lm1<-lmer(Emergediffinsdtrt ~ sdtrt*Var + (1 | Rep/Exp), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt | Var)
ab<-summary(lsm1)
ab<-as.data.frame(ab$lsmeans)
agh<-ab
gh<-ggplot(agh, aes(y=lsmean, x=Var, color=sdtrt)
)+ 
geom_point(position=position_dodge(width=0.21))+ 
geom_errorbar(aes(ymin=agh$lsmean-1.96*agh$SE, ymax=agh$lsmean+1.96*agh$SE), width=0.2, position=position_dodge(width=0.21))+
  labs(y="Greenhouse Emergence \n Relative to NTC", x="Soybean Variety", color="Seed Treament")+
theme(axis.title=element_text(size=14), axis.text=element_text(size=12), legend.title=element_text(size=14), legend.text=element_text(size=12))

#2015
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CAD.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") #& !(Y$sdtrt=="CON") 
           & (Y$Year=="2015")
           )
Y3$var<-as.factor(Y3$var)
lm1<-lmer(RDWcont ~ sdtrt*var*YL + (1 | rep/YL), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt:var | var)
a<-summary(lsm1$lsmeans)
a<-as.data.frame(a)
a13<-subset(a, !(a$var=="3") & !(a$var=="4"))

grdw<-ggplot(a13, aes(y=lsmean, x=var, color=sdtrt)
)+
  geom_point(position=position_dodge(width=0.21))+
   geom_errorbar(aes( ymin=a13$lsmean-1.96*a13$SE, ymax=a13$lsmean+1.96*a13$SE), width=0.2, position=position_dodge(width=0.21))+
  labs(y="Field Root Dry Weight \n Relative to NTC", x="Soybean Variety", color="Seed Treament")+
theme(axis.title=element_text(size=14), axis.text=element_text(size=12), legend.title=element_text(size=14), legend.text=element_text(size=12))

#GH 
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/GHData.csv"))
Y3<-subset(Y, !(Y$RDWdiffinsdtrt=="NA") & !(Y$Var=="Sloan") 
           #& (Y$PathTitle=="Control")
           #& !(Y$sdtrt=="CON")
           )
Y3$Var<-as.factor(Y3$Var)
lm1<-lmer(RDWdiffinsdtrt ~ sdtrt*Var + (1 | Rep/Exp), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt | Var)
a<-summary(lsm1)
a<-as.data.frame(a$lsmeans)
agh1<-a

ghrdw<-ggplot(agh1, aes(y=lsmean, x=Var, color=sdtrt)
)+ geom_point(position=position_dodge(width=0.21))+
geom_errorbar( aes(ymin=a$lsmean-1.96*a$SE, ymax=a$lsmean+1.96*a$SE, width=0.2), position=position_dodge(width=0.21))+
labs(y="Greenhouse Root Dry Weight \n Relative to NTC", x="Soybean Variety", color="Seed Treament")+
theme(axis.title=element_text(size=14), axis.text=element_text(size=12), legend.title=element_text(size=14), legend.text=element_text(size=12))

structure(ghrdw)
pq<-multiplot(g, grdw, gh, ghrdw, cols=2)

```

``{r, echo=FALSE}

#2014
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CADnoCON.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") & !(Y$sdtrt=="CON") 
           & (Y$Year=="2014")
           )
Y3$var<-as.factor(Y3$var)
lm1<-lmer(RDWcont ~ sdtrt*var*YL + (1 | rep/YL), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt:var | var)
a<-summary(lsm1)
a<-as.data.frame(a)
a12<-subset(a, !(a$lsmeans.var=="3") & !(a$lsmeans.var=="4"))

grdw14<-ggplot(a12, aes(y=lsmeans.lsmean, x=lsmeans.var, color=lsmeans.sdtrt)
)+
  geom_point()+
  labs(y="RDW 2014")

#2014
Y <- (read.csv("/Users/devonrossman/Desktop/CSVforR/SoySdTrt/CSVFiles/CADnoCON.csv"))
Y3<-subset(Y, !(Y$Diff8=="NA") & !(Y$sdtrt=="CON") 
           & (Y$Year=="2014")
           )
Y3$var<-as.factor(Y3$var)
lm1<-lmer(Scpubcont ~ sdtrt*var*YL + (1 | rep/YL), data=Y3)
lsm1<-lsmeans(lm1, pairwise~sdtrt:var | var)
a<-summary(lsm1)
a<-as.data.frame(a)
a12<-subset(a, !(a$lsmeans.var=="3") & !(a$lsmeans.var=="4"))

g14<-ggplot(a12, aes(y=lsmeans.lsmean, x=lsmeans.var, color=lsmeans.sdtrt)
)+
  geom_point()+
  labs(y="Plant Stand Relative to NTC 2014")



```
